---
title: "Seminar 2"
format: html
editor: visual
author: Matilda Kuusi
date: today
echo: false
bibliography: Human_variation_in_the_shape_of.bib
---

# Instructions

Find an interesting dataset on DataDryad.org (or another data repository) and download it. Make an RStudio project to reproduce one or more of the figures in the paper associated with the dataset, making your analysis as reproducible as possible by using (at least)

-   git and GitHub

-   renv for package management

-   Best practice for comments and code style

-   here package for helping load data

-   quarto or Rmarkdown for the document (reference the data source and the original paper)

```{r}
#| label: load-packages
#| include: false

library(tidyverse) # for ggplot2
library(here)      # for help finding files
library(lubridate) # for handling dates & times
library(gt)        # for tables
library(usethis)   # for git

```

```{r}
#| label: load-data
#| include: false

#reading the csv file
data1 <- read_csv(here(file = "data/Dataset.csv"))
```

```{r}
#| label: model1
#| include: false

#data for inlet, midplane, outlet

data_fig <- data1|>
  select(inlet.ML, inlet.AP, midplane.ML, midplane.AP, outlet.ML, outlet.AP, Region)
```

```{r}
#| label: calling functions

#run functions for inlet, midplane, outlet
source("APML_function.R")
inlet_APML <- APML_div(data_fig, "inlet.AP", "inlet.ML")
outlet_APML <- APML_div(data_fig, "outlet.AP", "outlet.ML")
midplane_APML <- APML_div(data_fig,"midplane.AP","midplane.ML")
```

```{r}
#| label: dataframe
#| include: false

#dataframe with AP/ML in each region
df <- data.frame(inlet_APML, midplane_APML, outlet_APML, data1$Region)
df
```

# Figures

Variation in the inlet (a), midplane (b), and outlet (c) indices within the four major geographical regions @Betti2018.

```{r}
#| label: figures

data_a <- df$inlet_APML
data_b <- df$midplane_APML
data_c <- df$outlet_APML

#splitting the group labels to fit the graph
groups <- gsub(" ", "\n", df$data1.Region)

#boxplots for inlet, midplan, and outlet AP/ML
#in each region

groups <- gsub(" ", "\n", df$data1.Region)

source("box_plot_function.R")
box_plot(data_a, groups, "(a)", "inlet AP/ML")
box_plot(data_b,groups, "(b)", "midline AP/ML")
box_plot(data_c,groups, "(c)", "outlet AP/ML")

```
